### 2017-10-26 draft.Rmd
Add files via upload

```{r include = FALSE, cache = FALSE}
load("~/.RData")
```

@@

Suppose $\alpha = 0.20$, we can find out the threshold for weekdays is $\phi_{obs} = 0.0081$, whereas the threshold for weekend is $\phi_{pred} = 0.0112$ and the proportions of points are approximately $\alpha$ using rank respectively (as plot showed below).

For instance, when $\alpha = 0.20$, we need top 6 ranks out of 34 for weekdays to have propotion of segments identified as hotspot approximately 0.2, whereas we need top 3 out of 17 for weekend. It is reasonable to use rank system instead of just number of segments needed. When segments have same ranks, they should be equally influential and included or excluded in the setting.

```{r fig.height = 3.5, fig.width = 3.5, fig.show = "hold", results = "asis"}
library(dplyr)
alpha = 0.20
t1 <- data.frame(lvl.set(z1, alpha))
t2 <- data.frame(lvl.set(z2, alpha))

@@

A sequence of $\alpha$ values is used to observe the pattern in different levels, $\alpha \in [0, 1]$ with length of interval 0.01. $Y$-axis is the cumulative proportion of crashes in hotspots and $X$-axis is level of $\alpha$. Suppose $\alpha = 0.3$, roughly 12.6% and 15.1% of crashes in weekend and weekdays respectively happened on the top 30% of Logmile segments (figure showed bottom left).

@@

For two distribution given different time period, $D = 0.0567 < D_{0.05} = 0.1911$, shows no significant difference in distributions. The maximal distance happens at $\alpha$ level 0.95, 0.96 and 0.97 (figure showed at bottom right).

@@

par(family = "serif")
plot(x = z1.lvl$alpha, y = z1.lvl$pct.events, type = "s", 
     xlab = expression(alpha), ylab = "%events in HS")
lines(x = z2.lvl$alpha, y = z2.lvl$pct.events, type = "s", col = 4)
abline(v = 0.3, col = "darkgrey")
text(x = c(0.3, 0.3), 
     y = c(z1.lvl[alpha == 0.3,]$pct.events,z2.lvl[alpha == 0.3,]$pct.events),
     labels = round(c(z1.lvl[alpha == 0.3,]$pct.events, z2.lvl[alpha == 0.3,]$pct.events),4), 
     pos = c(3,1), col = c(1, 4))

par(family = "serif")
plot(x = alpha, y = abs(t$d), type = "s", xlab = expression(alpha), ylab = "distance")
abline(h = 0, col = "darkgray")
segments(x0 = 0.96, y0 = t$max.d, y1 = 0, col = "darkgray")
text(x = 0.96, y = t$max.d, labels = round(t$max.d, 5), pos = 3)
```

plot on the bottom left, it is plotted thresholds against true proportion of segments will be identified as hotspots. For instance, under the same threshold 0.007, top 26.47% of segments have highest ranks on crashes will be hotspots for weekdays whereas top 35.29% of segments will be hotspots for weekends.

Plot on the bottom right, it shows the percentage of matched segments during weekdays and weekend under different levels of $\alpha$. When top 10% of segments are identified as hotspots in both period, 33.33% of segments in individual period are matched. While $\alpha$ increases to 0.2, 71.43% of segments in these periods are matched.

```{r fig.height = 3.5, fig.width = 3.5, fig.show = "hold", results = "asis"}
par(family = "serif")
plot(x = z1.lvl$thres, y = z1.lvl$level, type = "s", 
     xlab = "threshold", ylab = "%segments id as HS", 
     xlim = c(0, max(z1.lvl$thres, z2.lvl$thres)))
lines(x = z2.lvl$thres, y = z2.lvl$level, type = "s", col = 4)
abline(v = 0.007, col = "darkgrey")
text(x = c(0.007, 0.007), y = c(z1.lvl[alpha == 0.29,]$level, z2.lvl[alpha == 0.4,]$level),
     labels = round(c(z1.lvl[alpha == 0.29,]$level, z2.lvl[alpha == 0.4,]$level),4), 
     col = c(1, 4), pos = 3)
legend("topright", c("wk", "wkd"), col = c(1, 4), lty = 1)

@@

Relative distribution of percentage of crashes on weekdays and weekend (bottom left and bottom right). If two distributions have similar crash rates across different segments, ratios of two distributions under the same $alpha$ level should be equal to 1. In here, we can perform a Kolmogorov-Smirnov test to see the magnitude of diversity by comparing relative distribution to uniform distribution. On the bottom right is the result of converting relative and uniform distributions to cumulative probability functions respectively (black represents uniform, blue represents our relative distribution and red is the confidence band for our relativef distribution).
Either from a confidence band or KS test perspective, both results show no difference in distributions. The uniform lies within the confidence bands, and $\operatorname{max}_x|S_i(x)-S_j(x)|$, where $S_i(x)$ here stands for relative distribution and $S_j(x)$ is uniform, is $0.1137 < D_{0.05} = 0.1971$.

@@

c.alpha <- sqrt(-0.5*log(0.05/2)) 
bound <- c.alpha*sqrt(1/95+1/95)
low <- cumsum(r1[is.finite(r1)])-bound
up <- cumsum(r1[is.finite(r1)])+bound
low[low<0]=0
up[up>1]=1
lines(x = alpha[is.finite(r)], y = low, type = "s", col = 2)
lines(x = alpha[is.finite(r)], y = up, type = "s", col = 2)
```

@@

```{r}
par(family = "serif")
ds <- cumsum(r1[is.finite(r1)])-cumsum(r2)
plot(x = alpha[is.finite(r)], y = ds, cex = 0, xlab = expression(alpha),
     ylab = "distance in distribution", ylim = c(-1, 1))
segments(x0 = alpha[is.finite(r)], y0 = ds, y1 = 0)
lines(x = alpha[is.finite(r)], y = rep(bound, 95), type = "s", col = 2)
lines(x = alpha[is.finite(r)], y = rep(-bound, 95), type = "s", col = 2)
```

@@

try different day of week (i.e. Monday, Tuesday, and etc.), months, or different time in a day

>>>>

```{r include = FALSE, cache = FALSE}
load("~/all_plot.RData")
```

@@

Suppose $\alpha = 0.05$, we can find out the threshold for weekdays is $\phi_{obs} = 0.0032$, whereas the threshold for weekend is $\phi_{pred} = 0.0039$ and the proportions of points are approximately $\alpha$ respectively (as plot showed below).

When $\alpha = 0.05$, we need to have propotion of segments identified as hotspot approximately 0.2 for weekdays and weekend. We also need to consider ties (have the same rank) and should exlude or include these segments with the same rank simutaneously in the setting. The true proportions (levels) of segments for weekdays and weekend are 0.048 and 0.037 respectively.

```{r fig.height = 3.5, fig.width = 3.5, fig.show = "hold", results = "asis"}
library(dplyr)
alpha = 0.05
t1 <- data.frame(lvl.set(z1, alpha))
t2 <- data.frame(lvl.set(z2, alpha))

@@

A sequence of $\alpha$ values is used to observe the pattern in different levels, $\alpha \in [0, 1]$ with length of interval 0.01. $Y$-axis is the cumulative proportion of crashes in hotspots and $X$-axis is level of $\alpha$. Suppose $\alpha = 0.18$, roughly 82.26% and 86.92% of crashes in weekend and weekdays respectively happened on the top 18% of Logmile segments (figure showed bottom left).

@@

For two distribution given different time period, $D = 0.0851 < D_{0.05} = 0.1911$, shows no significant difference in distributions. The maximal distance happens at $\alpha$ level 0.11 (figure showed at bottom right).

@@

par(family = "serif")
plot(x = z1.lvl$alpha, y = z1.lvl$pct.events, type = "s", 
     xlab = expression(alpha), ylab = "%events in HS")
lines(x = z2.lvl$alpha, y = z2.lvl$pct.events, type = "s", col = 4)
abline(v = 0.18, col = "darkgrey")
text(x = c(0.18, 0.18), 
     y = c(z1.lvl[alpha == 0.18,]$pct.events,z2.lvl[alpha == 0.18,]$pct.events),
     labels = round(c(z1.lvl[alpha == 0.18,]$pct.events, z2.lvl[alpha == 0.18,]$pct.events),4), 
     pos = 3, col = c(1, 4))
legend("bottomright", c("wk", "wkd"), col = c(1, 4), lty = 1)

par(family = "serif")
plot(x = alpha, y = abs(t$d), type = "s", xlab = expression(alpha), ylab = "distance")
abline(h = 0, col = "darkgray")
```

plot on the bottom left, it is plotted thresholds against true proportion of segments will be identified as hotspots. For instance, under the same threshold 0.007, top 0.98% of segments have highest ranks on crashes will be hotspots for weekdays whereas top 0.82% of segments will be hotspots for weekends.

Plot on the bottom right, it shows the percentage of matched segments during weekdays and weekend under different levels of $\alpha$. When top 10% of segments are identified as hotspots in both period, 47.93% of segments in individual period are matched. While $\alpha$ increases to 0.2, 59.03% of segments in these periods are matched.

```{r fig.height = 3.5, fig.width = 3.5, fig.show = "hold", results = "asis"}
par(family = "serif")
plot(x = z1.lvl$thres, y = z1.lvl$level, type = "s", 
     xlab = "threshold", ylab = "%segments id as HS", 
     xlim = c(0, max(z1.lvl$thres, z2.lvl$thres)))
lines(x = z2.lvl$thres, y = z2.lvl$level, type = "s", col = 4)
abline(v = 0.007, col = "darkgrey")
text(x = c(0.007, 0.007), y = c(z1.lvl[alpha == 0.01,]$level, z2.lvl[alpha == 0.01,]$level),
     labels = round(c(z1.lvl[alpha == 0.01,]$level, z2.lvl[alpha == 0.01,]$level),4), 
     col = c(1, 4), pos = c(1,3))
legend("topright", c("wk", "wkd"), col = c(1, 4), lty = 1)

@@

Relative distribution of percentage of crashes on weekdays and weekend (bottom left and bottom right). If two distributions have similar crash rates across different segments, ratios of two distributions under the same $alpha$ level should be equal to 1. In here, we can perform a Kolmogorov-Smirnov test to see the magnitude of diversity by comparing relative distribution to uniform distribution. On the bottom right is the result of converting relative and uniform distributions to cumulative probability functions respectively (black represents uniform, blue represents our relative distribution and red is the confidence band for our relativef distribution).
Either from a confidence band or KS test perspective, both results show no difference in distributions. The uniform lies within the confidence bands, and $\operatorname{max}_x|S_i(x)-S_j(x)|$, where $S_i(x)$ here stands for relative distribution and $S_j(x)$ is uniform, is $0.0037 < D_{0.05} = 0.1921$.

@@

c.alpha <- sqrt(-0.5*log(0.05/2)) 
bound <- c.alpha*sqrt(1/100+1/100)
low <- cumsum(r1[is.finite(r1)])-bound
up <- cumsum(r1[is.finite(r1)])+bound
low[low<0]=0
up[up>1]=1
lines(x = alpha[is.finite(r)], y = low, type = "s", col = 2)
lines(x = alpha[is.finite(r)], y = up, type = "s", col = 2)
```

@@

```{r}
par(family = "serif")
ds <- cumsum(r1[is.finite(r1)])-cumsum(r2)
plot(x = alpha[is.finite(r)], y = ds, cex = 0, xlab = expression(alpha),
     ylab = "distance in distribution", ylim = c(-1, 1))
segments(x0 = alpha[is.finite(r)], y0 = ds, y1 = 0)
lines(x = alpha[is.finite(r)], y = rep(bound, 100), type = "s", col = 2)
lines(x = alpha[is.finite(r)], y = rep(-bound, 100), type = "s", col = 2)
```

@@

see day of week performance.

```{r include = FALSE, cache = FALSE}
load("~/dow.RData")
```

the summary table below shows the detail for each day of week when $\alpha = 0.05$. $Level$ is the true proportion of segments that closer and less than size $\alpha$; $nseg$ represents total number of segments needed to reach the level (or above the threshold), $pct.events$ is the proportion of events (sum of events in $nseg$); $thres$ is the threshold (lowest percentage of events within the $level$); $DayOfWeekUSA$ starts from Sunday (1) to Saturday (7).

```{r}
library(knitr)
kable(out %>% mutate(DayOfWeekUSA = time) %>% select(-time))
```

here's the distribution for the summary table showed previously. $level$ is made of the ratio of blue dots to total segments; $nseg$ is the number of blue dots; grey horizontal line is the threshold; total proportion of events happened on these blue dots (hotspots) are $pct.events$.

```{r}
library(ggplot2)
ggplot(data = week, mapping = aes(x = Logmile, y = p)) +
  geom_segment(aes(xend = Logmile, yend = 0)) + 
  geom_hline(aes(yintercept=hl), data=hline.dat, col = "darkgray") + 
  geom_point(data = point.dat, aes(x = Logmile, y = p), col = 4) + 
  facet_grid(DayOfWeekUSA~.)
```

recall from a surveillance plot, its x-axis represents the proportion of segments identified as hotspots ($\alpha$) or distance between segments because of constant interval, and its y-axis represents proportion of events happened in these hotspots.

we use KS test to see the significance in distributions of days of week from this surveillance perspective.

no significance in distribution 
\begin{table}[ht]\centering\begin{tabular}{rllrl}
\hline 1 & Mon & Tue, Wed, Thu, Fri \\
       2 & Tue & Wed, Thu, Fri \\
       3 & Wed & Thu, Fri \\
\hline\end{tabular}\end{table}

#data separation given different time

only for original data, without any setting

ks test: route 71, 2015 jan ~ dec (crtical point: 0.0449)
\begin{table}[ht]\centering\begin{tabular}{rllrl}
\hline Same \\
       1 & Jan & Jul, Sep, Oct\\
       2 & Mar & Sep, Oct\\
       3 & May & Aug\\
       4 & Jul & Sep\\
       5 & Sep & Oct\\
       6 & Nov & Dec\\
\hline\end{tabular}\end{table}

ks test: route 71, 2015 sun ~ sat (crtical point: 0.0449)
\begin{table}[ht]\centering\begin{tabular}{rllrl}
\hline Same \\
       1 & mon & tue (0.0304), wed (0.0407), fri (0.0286)\\
       2 & tue & wed (0.0418), thu (0.0433), fri (0.0314), sat (0.0399)\\
       3 & wed & thu (0.0366), fri (0.0427), sat (0.0371)\\
       Diff\\
       1 & mon & thu (0.0484), sat (0.0513), sun (0.0746)\\
       2 & tue & sun (0.0673)\\
       3 & wed & sun (0.0831)\\
       4 & thu & fri (0.0470), sat (0.0470), sun (0.0961)\\
       5 & fri & sat (0.0497), sun (0.0644)\\
       6 & sat & sun (0.0842)\\
\hline\end{tabular}\end{table}

result 1 (tod: 2 groups) (critical point = 0.0449)
\begin{table}[ht]\centering\begin{tabular}{rllrl}
\hline Diff \\
       1 & 0am-12pm, 12pm-0am (0.0494)\\
\hline\end{tabular}\end{table}

result 2 (tod: 3 groups) (critical point = 0.0449)
\begin{table}[ht]\centering\begin{tabular}{rllrl}
\hline Same \\
       1 & 8-16 & 16-24 (0.0370)\\
       Diff \\
       1 & 0-8 & 8-16 (0.1077)\\
       2 & 8-16 & 16-24 (0.0370)\\
\hline\end{tabular}\end{table}

result 3 (tod: 6 groups) (critical point = 0.0449)
\begin{table}[ht]\centering\begin{tabular}{rllrl}
\hline Same \\
       1 & 8-12 & 16-20 (0.0413)\\
       2 & 12-16 & 16-20 (0.0427)\\
       Diff \\
       1 & 0-4 & 4-8 (0.0863), 8-12 (0.1338), 12-16 (0.1469), 16-20 (0.1593), 20-24 (0.1481)\\
       2 & 4-8 & 8-12 (0.0918), 12-16 (0.0844), 16-20 (0.1009), 20-24 (0.0730)\\
       3 & 8-12 & 12-16 (0.0588), 20-24 (0.0642)\\
       4 & 12-16 & 20-24 (0.0499)\\
       5 & 16-20 & 20-24 (0.0639)\\
\hline\end{tabular}\end{table}

result 4 (tod: 12 groups) (critical point = 0.0449)
\begin{table}[ht]\centering\begin{tabular}{rllrl}
\hline Same \\
       1 & 10-12 & 12-14\\
       2 & 12-14 & 16-18, 18-20\\
       3 & 16-18 & 18-20\\
       4 & 18-20 & 20-22\\
\hline\end{tabular}\end{table}
